Neural Networks Loss Landscape Convergence in Different Low-Dimensional Spaces

### 2025-03-13 paper/main.tex
Universal commits presents...

\textbf{Outline.} The rest of the paper is organized as follows...but I don't know how yet.

>>>>

\textbf{Outline.} The rest of the paper is organized as follows. Section 2 divides existing results into some
topics, highlighting their key contributions and findings. Section 3 considers general notation and
some preliminary calculations. In Section 4, we provide theoretical bounds on the hessian and losses
difference norms. Empirical study of the obtained results is given in Section 5. We summarize and
present the results in Sections 6 and 7. Additional experiments and proofs of theorems are included
in the Appendix A.
